### 2019-08-20 reports/thesis/chapters/5_inference.tex
Use 1 sigma confidence interval

\begin{figure}
  \centering
  \includegraphics[width=\mainSize]{../figures/inference/BandwidthSelection2_ruleOfThumb.eps}
  \caption{An identity link gamma GLM was fitted onto the relationship between the optimal bandwidth and $n^{-1/5}$ from the experimental data. The dotted lines shows the 95\% prediction interval.}
  \label{fig:inference_BandwidthSelection2_ruleOfThumb}
\end{figure}

@@

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/NullIidEmpirical_nullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/NullIidMedianIqr_nullMean.eps}
        \caption{Median}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/NullIidMeanVar_nullMean.eps}
        \caption{Mean}
      \end{subfigure}
    }
  \caption{Different types of central tendency estimators were used on $\pi r^2$ standard Normal random variables. Shown are the sampling distributions from 100 repeats. The dotted lines show the 95\% confidence interval for the sample mean.}
  \label{fig:inference_NullIidMean}
\end{figure}

\begin{figure}
  \centering
    \centerline{
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/NullIidEmpirical_nullStd.eps}
        \caption{Empirical null std.}
      \end{subfigure}
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/NullIidMadMode_nullStd.eps}
        \caption{MAD mode}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/NullIidMedianIqr_nullStd.eps}
        \caption{IQR}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/NullIidMeanVar_nullStd.eps}
        \caption{Standard deviation}
      \end{subfigure}
    }
  \caption{Different types of statistical dispersion estimators were used on $\pi r^2$ standard Normal random variables. Shown are the sampling distributions from 100 repeats. The dotted lines show the 95\% confidence interval for the sample variance.}
  \label{fig:inference_NullIidStd}
\end{figure}

\begin{figure}
  \centering
    \centerline{
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/NullIidMixtureEmpirical_nullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/NullIidMixtureMedianIqr_nullMean.eps}
        \caption{Median}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/NullIidMixtureMeanVar_nullMean.eps}
        \caption{Mean}
      \end{subfigure}
    }
  \caption{Different types of central tendency estimators were used on $\pi r^2$ mixture of Gaussian random variables. The random variable has distribution $\normal(0,1)$ with probability $0.9$ and $\normal(3,1)$ with probability $0.1$. Shown are the sampling distributions from 100 repeats. The dotted lines show the 95\% confidence interval for the sample mean.}
  \label{fig:inference_NullIidMixtureMean}
\end{figure}

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/NullIidMixtureEmpirical_nullStd.eps}
        \caption{Empirical null std.}
      \end{subfigure}
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/NullIidMixtureMadMode_nullStd.eps}
        \caption{MAD mode}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/NullIidMixtureMedianIqr_nullStd.eps}
        \caption{IQR}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/NullIidMixtureMeanVar_nullStd.eps}
        \caption{Standard deviation}
      \end{subfigure}
    }
  \caption{Different types of statistical dispersion estimators were used on $\pi r^2$ mixture of Gaussian random variables. The random variable has distribution $\normal(0,1)$ with probability $0.9$ and $\normal(3,1)$ with probability $0.1$. Shown are the sampling distributions from 100 repeats. The dotted lines show the 95\% confidence interval for the sample variance.}
  \label{fig:inference_NullIidMixtureStd}
\end{figure}

@@

\begin{figure}
  \centering
  \centerline{
  \begin{subfigure}[b]{\subSize}
    \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianEmpirical_mean.eps}
    \caption{Empirical Null}
  \end{subfigure}
  \begin{subfigure}[b]{\subSize}
    \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianMadMode_mean.eps}
    \caption{MAD Mode Null}
  \end{subfigure}
  }
  \centerline{
    \begin{subfigure}[b]{\subSize}
    \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianMedianIqr_mean.eps}
    \caption{Median IQR Null}
  \end{subfigure}
  \begin{subfigure}[b]{\subSize}
    \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianMeanVar_mean.eps}
    \caption{Mean Var Null}
  \end{subfigure}
  }
  \caption{The within image sample \emph{mean} of the test statistics in a filtered Gaussian image of size $256\times256$. The box plots summarise the 100 repeats of the experiment. The dashed lines show the 95\% confidence interval using standard tests, assuming independence.}
  \label{fig:inference_AllNullGaussian_mean}
\end{figure}

\begin{figure}
  \centering
  \centerline{
  \begin{subfigure}[b]{\subSize}
    \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianEmpirical_variance.eps}
    \caption{Empirical Null}
  \end{subfigure}
  \begin{subfigure}[b]{\subSize}
    \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianMadMode_variance.eps}
    \caption{MAD Mode Null}
  \end{subfigure}
  }
  \centerline{
    \begin{subfigure}[b]{\subSize}
    \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianMedianIqr_variance.eps}
    \caption{Median IQR Null}
  \end{subfigure}
  \begin{subfigure}[b]{\subSize}
    \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianMeanVar_variance.eps}
    \caption{Mean Var Null}
  \end{subfigure}
  }
  \caption{The within image sample \emph{standard deviation} of the test statistics in a filtered Gaussian image of size $256\times256$. The box plots summarise the 100 repeats of the experiment. The dashed lines show the 95\% confidence interval using standard tests, assuming independence.}
  \label{fig:inference_AllNullGaussian_var}
\end{figure}

\begin{figure}
  \centering
  \centerline{
  \begin{subfigure}[b]{\subSize}
    \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianEmpirical_kurtosis.eps}
    \caption{Empirical Null}
  \end{subfigure}
  \begin{subfigure}[b]{\subSize}
    \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianMadMode_kurtosis.eps}
    \caption{MAD Mode Null}
  \end{subfigure}
  }
  \centerline{
    \begin{subfigure}[b]{\subSize}
    \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianMedianIqr_kurtosis.eps}
    \caption{Median IQR Null}
  \end{subfigure}
  \begin{subfigure}[b]{\subSize}
    \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianMeanVar_kurtosis.eps}
    \caption{Mean Var Null}
  \end{subfigure}
  }
  \caption{The within image sample \emph{kurtosis} of the test statistics in a filtered Gaussian image of size $256\times256$. The box plots summarise the 100 repeats of the experiment. The dashed lines show the 95\% confidence interval using standard tests, assuming independence.}
  \label{fig:inference_AllNullGaussian_kurtosis}
\end{figure}

\begin{figure}
  \centering
  \centerline{
  \begin{subfigure}[b]{\subSize}
    \includegraphics[width=\textwidth]{../figures/inference/AllNullPlaneEmpirical_mean.eps}
    \caption{Empirical Null}
  \end{subfigure}
  \begin{subfigure}[b]{\subSize}
    \includegraphics[width=\textwidth]{../figures/inference/AllNullPlaneMadMode_mean.eps}
    \caption{MAD Mode Null}
  \end{subfigure}
  }
  \centerline{
    \begin{subfigure}[b]{\subSize}
    \includegraphics[width=\textwidth]{../figures/inference/AllNullPlaneMedianIqr_mean.eps}
    \caption{Median IQR Null}
  \end{subfigure}
  \begin{subfigure}[b]{\subSize}
    \includegraphics[width=\textwidth]{../figures/inference/AllNullPlaneMeanVar_mean.eps}
    \caption{Mean Var Null}
  \end{subfigure}
  }
  \caption{The within image sample \emph{mean} of the test statistics in a filtered \emph{contaminated} Gaussian image of size $256\times256$. The box plots summarise the 100 repeats of the experiment. The dashed lines show the 95\% confidence interval using standard tests, assuming independence.}
  \label{fig:inference_AllNullPlane_mean}
\end{figure}

\begin{figure}
  \centering
  \centerline{
  \begin{subfigure}[b]{\subSize}
    \includegraphics[width=\textwidth]{../figures/inference/AllNullPlaneEmpirical_variance.eps}
    \caption{Empirical Null}
  \end{subfigure}
  \begin{subfigure}[b]{\subSize}
    \includegraphics[width=\textwidth]{../figures/inference/AllNullPlaneMadMode_variance.eps}
    \caption{MAD Mode Null}
  \end{subfigure}
  }
  \centerline{
    \begin{subfigure}[b]{\subSize}
    \includegraphics[width=\textwidth]{../figures/inference/AllNullPlaneMedianIqr_variance.eps}
    \caption{Median IQR Null}
  \end{subfigure}
  \begin{subfigure}[b]{\subSize}
    \includegraphics[width=\textwidth]{../figures/inference/AllNullPlaneMeanVar_variance.eps}
    \caption{Mean Var Null}
  \end{subfigure}
  }
  \caption{The within image sample \emph{standard deviation} of the test statistics in a filtered \emph{contaminated} Gaussian image of size $256\times256$. The box plots summarise the 100 repeats of the experiment. The dashed lines show the 95\% confidence interval using standard tests, assuming independence.}
  \label{fig:inference_AllNullPlane_var}
\end{figure}

\begin{figure}
  \centering
  \centerline{
  \begin{subfigure}[b]{\subSize}
    \includegraphics[width=\textwidth]{../figures/inference/AllNullPlaneEmpirical_kurtosis.eps}
    \caption{Empirical Null}
  \end{subfigure}
  \begin{subfigure}[b]{\subSize}
    \includegraphics[width=\textwidth]{../figures/inference/AllNullPlaneMadMode_kurtosis.eps}
    \caption{MAD Mode Null}
  \end{subfigure}
  }
  \centerline{
    \begin{subfigure}[b]{\subSize}
    \includegraphics[width=\textwidth]{../figures/inference/AllNullPlaneMedianIqr_kurtosis.eps}
    \caption{Median IQR Null}
  \end{subfigure}
  \begin{subfigure}[b]{\subSize}
    \includegraphics[width=\textwidth]{../figures/inference/AllNullPlaneMeanVar_kurtosis.eps}
    \caption{Mean Var Null}
  \end{subfigure}
  }
  \caption{The within image sample \emph{kurtosis} of the test statistics in a filtered \emph{contaminated} Gaussian image of size $256\times256$. The box plots summarise the 100 repeats of the experiment. The dashed lines show the 95\% confidence interval using standard tests, assuming independence.}
  \label{fig:inference_AllNullPlane_kurtosis}
\end{figure}

@@

\begin{figure}
  \centering
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectAltDustEmpirical_roc.eps}
        \caption{AUC}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectAltDustEmpirical_type1.eps}
        \label{fig:inference_DefectSimulationDust_type1}
        \caption{Type 1 error}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectAltDustEmpirical_type2.eps}
        \caption{Type 2 error}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectAltDustEmpirical_fdr.eps}
        \caption{FDR}
        \label{fig:inference_DefectSimulationDust_fdr}
      \end{subfigure}
    }
  \caption{AUC and various errors obtained when conducting hypothesis test on a \emph{empirical null} filtered contaminated image of a $256 \times 256$ salt defected Gaussian image. In a), the upper/lower dot dashed line shows the resulting mean AUC when testing on a defected image before/after contamination respectively. In b) c) d) the dashed lines shows the 95\% empirical confidence interval of the resulting error when testing the defected image before contamination. The filter used a kernel radius of 20. Defected pixels have the distribution $\normal(\mu_1,1)$ where $\mu_1$ was varied in this experiment. The salt defect has density $\pi_1 = 0.1$. The contamination is such that the null distribution is $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$. The test was done at the 5\% FDR level. The box plot summarise the 100 repeats of the experiment.}
  \label{fig:inference_DefectSimulationDust}
\end{figure}

@@

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectRadiusLine_roc.eps}
        \caption{AUC}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectRadiusLine_type1.eps}
        \caption{Type 1 error}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectRadiusLine_type2.eps}
        \caption{Type 2 error}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectRadiusLine_fdr.eps}
        \caption{FDR}
      \end{subfigure}
    }
  \caption{AUC and various errors obtained when conducting hypothesis test on the filtered contaminated image of a $256 \times 256$ line defected Gaussian image using various kernel radiuses. The dashed lines show the resulting 95\% empirical confidence interval when the hypothesis test was done on the uncontaminated image. Defected pixels have the distribution $\normal(3,1)$. The line defect is 5 pixels thick. The contamination is such that the null distribution is $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$. The test was done at the 5\% FDR level. The box plot summarise the 100 repeats of the experiment.}
  \label{fig:inference_Experiment_DefectRadiusLine}
\end{figure}

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectRadiusSquare_roc.eps}
        \caption{AUC}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectRadiusSquare_type1.eps}
        \caption{Type 1 error}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectRadiusSquare_type2.eps}
        \caption{Type 2 error}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectRadiusSquare_fdr.eps}
        \caption{FDR}
      \end{subfigure}
    }
  \caption{AUC and various errors obtained when conducting hypothesis test on the filtered contaminated image of a $256 \times 256$ square defected Gaussian image using various kernel radiuses. The dashed lines show the resulting 95\% empirical confidence interval when the hypothesis test was done on the uncontaminated image. Defected pixels have the distribution $\normal(3,1)$. The square defect is $30\times 30$ pixels in size. The contamination is such that the null distribution is $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$. The test was done at the 5\% FDR level. The box plot summarise the 100 repeats of the experiment.}
  \label{fig:inference_Experiment_DefectRadiusSquare}
\end{figure}

>>>>

\begin{figure}
  \centering
  \includegraphics[width=\mainSize]{../figures/inference/BandwidthSelection2_ruleOfThumb.eps}
  \caption{An identity link gamma GLM was fitted onto the relationship between the optimal bandwidth and $n^{-1/5}$ from the experimental data. The dotted lines shows the 68\% prediction interval.}
  \label{fig:inference_BandwidthSelection2_ruleOfThumb}
\end{figure}

@@

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/NullIidEmpirical_nullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/NullIidMedianIqr_nullMean.eps}
        \caption{Median}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/NullIidMeanVar_nullMean.eps}
        \caption{Mean}
      \end{subfigure}
    }
  \caption{Different types of central tendency estimators were used on $\pi r^2$ standard Normal random variables. Shown are the sampling distributions from 100 repeats. The dotted lines show the 68\% confidence interval for the sample mean.}
  \label{fig:inference_NullIidMean}
\end{figure}

\begin{figure}
  \centering
    \centerline{
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/NullIidEmpirical_nullStd.eps}
        \caption{Empirical null std.}
      \end{subfigure}
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/NullIidMadMode_nullStd.eps}
        \caption{MAD mode}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/NullIidMedianIqr_nullStd.eps}
        \caption{IQR}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/NullIidMeanVar_nullStd.eps}
        \caption{Standard deviation}
      \end{subfigure}
    }
  \caption{Different types of statistical dispersion estimators were used on $\pi r^2$ standard Normal random variables. Shown are the sampling distributions from 100 repeats. The dotted lines show the 68\% confidence interval for the sample variance.}
  \label{fig:inference_NullIidStd}
\end{figure}

\begin{figure}
  \centering
    \centerline{
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/NullIidMixtureEmpirical_nullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/NullIidMixtureMedianIqr_nullMean.eps}
        \caption{Median}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/NullIidMixtureMeanVar_nullMean.eps}
        \caption{Mean}
      \end{subfigure}
    }
  \caption{Different types of central tendency estimators were used on $\pi r^2$ mixture of Gaussian random variables. The random variable has distribution $\normal(0,1)$ with probability $0.9$ and $\normal(3,1)$ with probability $0.1$. Shown are the sampling distributions from 100 repeats. The dotted lines show the 68\% confidence interval for the sample mean.}
  \label{fig:inference_NullIidMixtureMean}
\end{figure}

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/NullIidMixtureEmpirical_nullStd.eps}
        \caption{Empirical null std.}
      \end{subfigure}
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/NullIidMixtureMadMode_nullStd.eps}
        \caption{MAD mode}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/NullIidMixtureMedianIqr_nullStd.eps}
        \caption{IQR}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/NullIidMixtureMeanVar_nullStd.eps}
        \caption{Standard deviation}
      \end{subfigure}
    }
  \caption{Different types of statistical dispersion estimators were used on $\pi r^2$ mixture of Gaussian random variables. The random variable has distribution $\normal(0,1)$ with probability $0.9$ and $\normal(3,1)$ with probability $0.1$. Shown are the sampling distributions from 100 repeats. The dotted lines show the 68\% confidence interval for the sample variance.}
  \label{fig:inference_NullIidMixtureStd}
\end{figure}

@@

\begin{figure}
  \centering
  \centerline{
  \begin{subfigure}[b]{\subSize}
    \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianEmpirical_mean.eps}
    \caption{Empirical Null}
  \end{subfigure}
  \begin{subfigure}[b]{\subSize}
    \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianMadMode_mean.eps}
    \caption{MAD Mode Null}
  \end{subfigure}
  }
  \centerline{
    \begin{subfigure}[b]{\subSize}
    \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianMedianIqr_mean.eps}
    \caption{Median IQR Null}
  \end{subfigure}
  \begin{subfigure}[b]{\subSize}
    \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianMeanVar_mean.eps}
    \caption{Mean Var Null}
  \end{subfigure}
  }
  \caption{The within image sample \emph{mean} of the test statistics in a filtered Gaussian image of size $256\times256$. The box plots summarise the 100 repeats of the experiment. The dashed lines show the 68\% confidence interval using standard tests, assuming independence.}
  \label{fig:inference_AllNullGaussian_mean}
\end{figure}

\begin{figure}
  \centering
  \centerline{
  \begin{subfigure}[b]{\subSize}
    \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianEmpirical_variance.eps}
    \caption{Empirical Null}
  \end{subfigure}
  \begin{subfigure}[b]{\subSize}
    \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianMadMode_variance.eps}
    \caption{MAD Mode Null}
  \end{subfigure}
  }
  \centerline{
    \begin{subfigure}[b]{\subSize}
    \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianMedianIqr_variance.eps}
    \caption{Median IQR Null}
  \end{subfigure}
  \begin{subfigure}[b]{\subSize}
    \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianMeanVar_variance.eps}
    \caption{Mean Var Null}
  \end{subfigure}
  }
  \caption{The within image sample \emph{standard deviation} of the test statistics in a filtered Gaussian image of size $256\times256$. The box plots summarise the 100 repeats of the experiment. The dashed lines show the 68\% confidence interval using standard tests, assuming independence.}
  \label{fig:inference_AllNullGaussian_var}
\end{figure}

\begin{figure}
  \centering
  \centerline{
  \begin{subfigure}[b]{\subSize}
    \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianEmpirical_kurtosis.eps}
    \caption{Empirical Null}
  \end{subfigure}
  \begin{subfigure}[b]{\subSize}
    \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianMadMode_kurtosis.eps}
    \caption{MAD Mode Null}
  \end{subfigure}
  }
  \centerline{
    \begin{subfigure}[b]{\subSize}
    \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianMedianIqr_kurtosis.eps}
    \caption{Median IQR Null}
  \end{subfigure}
  \begin{subfigure}[b]{\subSize}
    \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianMeanVar_kurtosis.eps}
    \caption{Mean Var Null}
  \end{subfigure}
  }
  \caption{The within image sample \emph{kurtosis} of the test statistics in a filtered Gaussian image of size $256\times256$. The box plots summarise the 100 repeats of the experiment. The dashed lines show the 68\% confidence interval using standard tests, assuming independence.}
  \label{fig:inference_AllNullGaussian_kurtosis}
\end{figure}

\begin{figure}
  \centering
  \centerline{
  \begin{subfigure}[b]{\subSize}
    \includegraphics[width=\textwidth]{../figures/inference/AllNullPlaneEmpirical_mean.eps}
    \caption{Empirical Null}
  \end{subfigure}
  \begin{subfigure}[b]{\subSize}
    \includegraphics[width=\textwidth]{../figures/inference/AllNullPlaneMadMode_mean.eps}
    \caption{MAD Mode Null}
  \end{subfigure}
  }
  \centerline{
    \begin{subfigure}[b]{\subSize}
    \includegraphics[width=\textwidth]{../figures/inference/AllNullPlaneMedianIqr_mean.eps}
    \caption{Median IQR Null}
  \end{subfigure}
  \begin{subfigure}[b]{\subSize}
    \includegraphics[width=\textwidth]{../figures/inference/AllNullPlaneMeanVar_mean.eps}
    \caption{Mean Var Null}
  \end{subfigure}
  }
  \caption{The within image sample \emph{mean} of the test statistics in a filtered \emph{contaminated} Gaussian image of size $256\times256$. The box plots summarise the 100 repeats of the experiment. The dashed lines show the 68\% confidence interval using standard tests, assuming independence.}
  \label{fig:inference_AllNullPlane_mean}
\end{figure}

\begin{figure}
  \centering
  \centerline{
  \begin{subfigure}[b]{\subSize}
    \includegraphics[width=\textwidth]{../figures/inference/AllNullPlaneEmpirical_variance.eps}
    \caption{Empirical Null}
  \end{subfigure}
  \begin{subfigure}[b]{\subSize}
    \includegraphics[width=\textwidth]{../figures/inference/AllNullPlaneMadMode_variance.eps}
    \caption{MAD Mode Null}
  \end{subfigure}
  }
  \centerline{
    \begin{subfigure}[b]{\subSize}
    \includegraphics[width=\textwidth]{../figures/inference/AllNullPlaneMedianIqr_variance.eps}
    \caption{Median IQR Null}
  \end{subfigure}
  \begin{subfigure}[b]{\subSize}
    \includegraphics[width=\textwidth]{../figures/inference/AllNullPlaneMeanVar_variance.eps}
    \caption{Mean Var Null}
  \end{subfigure}
  }
  \caption{The within image sample \emph{standard deviation} of the test statistics in a filtered \emph{contaminated} Gaussian image of size $256\times256$. The box plots summarise the 100 repeats of the experiment. The dashed lines show the 68\% confidence interval using standard tests, assuming independence.}
  \label{fig:inference_AllNullPlane_var}
\end{figure}

\begin{figure}
  \centering
  \centerline{
  \begin{subfigure}[b]{\subSize}
    \includegraphics[width=\textwidth]{../figures/inference/AllNullPlaneEmpirical_kurtosis.eps}
    \caption{Empirical Null}
  \end{subfigure}
  \begin{subfigure}[b]{\subSize}
    \includegraphics[width=\textwidth]{../figures/inference/AllNullPlaneMadMode_kurtosis.eps}
    \caption{MAD Mode Null}
  \end{subfigure}
  }
  \centerline{
    \begin{subfigure}[b]{\subSize}
    \includegraphics[width=\textwidth]{../figures/inference/AllNullPlaneMedianIqr_kurtosis.eps}
    \caption{Median IQR Null}
  \end{subfigure}
  \begin{subfigure}[b]{\subSize}
    \includegraphics[width=\textwidth]{../figures/inference/AllNullPlaneMeanVar_kurtosis.eps}
    \caption{Mean Var Null}
  \end{subfigure}
  }
  \caption{The within image sample \emph{kurtosis} of the test statistics in a filtered \emph{contaminated} Gaussian image of size $256\times256$. The box plots summarise the 100 repeats of the experiment. The dashed lines show the 68\% confidence interval using standard tests, assuming independence.}
  \label{fig:inference_AllNullPlane_kurtosis}
\end{figure}

@@

\begin{figure}
  \centering
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectAltDustEmpirical_roc.eps}
        \caption{AUC}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectAltDustEmpirical_type1.eps}
        \label{fig:inference_DefectSimulationDust_type1}
        \caption{Type 1 error}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectAltDustEmpirical_type2.eps}
        \caption{Type 2 error}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectAltDustEmpirical_fdr.eps}
        \caption{FDR}
        \label{fig:inference_DefectSimulationDust_fdr}
      \end{subfigure}
    }
  \caption{AUC and various errors obtained when conducting hypothesis test on a \emph{empirical null} filtered contaminated image of a $256 \times 256$ salt defected Gaussian image. In a), the upper/lower dot dashed line shows the resulting mean AUC when testing on a defected image before/after contamination respectively. In b) c) d) the dashed lines shows the 68\% empirical confidence interval of the resulting error when testing the defected image before contamination. The filter used a kernel radius of 20. Defected pixels have the distribution $\normal(\mu_1,1)$ where $\mu_1$ was varied in this experiment. The salt defect has density $\pi_1 = 0.1$. The contamination is such that the null distribution is $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$. The test was done at the 5\% FDR level. The box plot summarise the 100 repeats of the experiment.}
  \label{fig:inference_DefectSimulationDust}
\end{figure}

@@

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectRadiusLine_roc.eps}
        \caption{AUC}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectRadiusLine_type1.eps}
        \caption{Type 1 error}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectRadiusLine_type2.eps}
        \caption{Type 2 error}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectRadiusLine_fdr.eps}
        \caption{FDR}
      \end{subfigure}
    }
  \caption{AUC and various errors obtained when conducting hypothesis test on the filtered contaminated image of a $256 \times 256$ line defected Gaussian image using various kernel radiuses. The dashed lines show the resulting 68\% empirical confidence interval when the hypothesis test was done on the uncontaminated image. Defected pixels have the distribution $\normal(3,1)$. The line defect is 5 pixels thick. The contamination is such that the null distribution is $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$. The test was done at the 5\% FDR level. The box plot summarise the 100 repeats of the experiment.}
  \label{fig:inference_Experiment_DefectRadiusLine}
\end{figure}

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectRadiusSquare_roc.eps}
        \caption{AUC}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectRadiusSquare_type1.eps}
        \caption{Type 1 error}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectRadiusSquare_type2.eps}
        \caption{Type 2 error}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectRadiusSquare_fdr.eps}
        \caption{FDR}
      \end{subfigure}
    }
  \caption{AUC and various errors obtained when conducting hypothesis test on the filtered contaminated image of a $256 \times 256$ square defected Gaussian image using various kernel radiuses. The dashed lines show the resulting 68\% empirical confidence interval when the hypothesis test was done on the uncontaminated image. Defected pixels have the distribution $\normal(3,1)$. The square defect is $30\times 30$ pixels in size. The contamination is such that the null distribution is $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$. The test was done at the 5\% FDR level. The box plot summarise the 100 repeats of the experiment.}
  \label{fig:inference_Experiment_DefectRadiusSquare}
\end{figure}
